---
title: "NHL R API client"
author: "Sanjna Shenoy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
runtime: shiny
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## NHL R Vignette

This vignette will explain briefly the functionality of the four functions in the nhlR package. The four functions are the `Outcome` function, the `YearlyRankings` function, the `GoalLocations` function, and the `DailySchedule` Function

## Daily Schedule function
This function creates a table of the games that were played on a given date, formatted as YYYY/MM/DD.

Example:
```{r, eval=FALSE}
DailySchedule("2018/11/12", API_KEY)
```
Once you obtain Game IDs from above, you can view the outcome in a clear table as well as Goal Locations using the functions described below
## Outcome Function

This function is designed to generate a table of results for a specific game.
Example:
```{r, eval=FALSE}
Outcome(game_id, API_KEY)
```

## Goal Locations Function

This function generates a map of the locations of where players were when goals occured. Scrolling over a plot point also allows the user to see information about the description of the goal

Example:
```{r, eval=FALSE}
GoalLocations(game_id, API_KEY)
```

## Yearly Rankings

This function generates a table of tem rankings per conference and division. Please note that only data from 2013-2018 is available using the trial version of the NHL API.

Example:
```{r, eval=FALSE}
YearlyRankings("2013", API_KEY)
```
